How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-05-07 tse-paper/content.tex
Include why Violin plots
Closes #47

Zooming in on only the 227 runs where PBE could synthesize a program,
\Cref{fig:recall-precision-examplecount-sythesisworked-PBE}
presents violin plots and averages of the precision, the recall
and the F$_{1}$-score
of these runs compared with the number of examples in the training set.
When the training set
size increases from one to two, recall, and F$_{1}$-score increase by
about 25\%, precision increases by about 10\%.
For two or more
training examples, recall, and F$_{1}$-score stay around 75\% and
precision around 96\%.

>>>>

Zooming in on only the 227 runs where PBE could synthesize a program,
\Cref{fig:recall-precision-examplecount-sythesisworked-PBE}
presents violin plots and averages of the precision, the recall
and the F$_{1}$-score
of these runs compared with the number of examples in the training set.
We chose violin plots to show spread in distributions of values. Specifically, we see an hour glass shape for training set size 1. In this case, it means that for recall (and F$_1$-score) there are about as many observations with low recall as there are with high. This is a striking difference to set size 2, where we have mostly correct extractions. When the training set
size increases from one to two, recall, and F$_{1}$-score increase by
about 25\%, precision increases by about 10\%.
For two or more
training examples, recall, and F$_{1}$-score stay around 75\% and
precision around 96\%.
